%-------------------------
% Resume in Latex
% Author : Andrew Ackerman
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Andrew Ackerman} \\ \vspace{1pt}
    \small 805-905-5948 $|$ \href{mailto:andrew.ackers@gmail.com}{andrew.ackers@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/andrew-ackerman-89743018b/}{linkedin.com/in/andrew-ackerman-89743018b} $|$
    \href{https://github.com/ackers93}{github.com/ackers93}
\end{center}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages:} Ruby, JavaScript, TypeScript, Python, Go, SQL, HTML, CSS \\
    \textbf{Frameworks:} Ruby on Rails, React, AngularJS, Django \\
    \textbf{Developer Tools:} Git, GitHub, GitLab, Bitbucket, Docker, VS Code, Azure, AWS, Kubernetes, SendGrid, Checkmarx, Postman, Jira, Notion \\
    \textbf{Libraries:} MagicTest, NumPy, Nokogiri, JSON, Devise, CanCanCan, RSpec, Capybara, RailsAdmin, Moment.js, jQuery, Chart.js, Redux, Fetch API, Axios, Jest, React Hook Form, Babel \\
    \textbf{Databases:} MySQL, PostgreSQL, SQLite \\
    \textbf{Specialties:} Backend development, REST API design, software security, cloud infrastructure, test automation
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Owner / Developer – JavaScript / HTML5 / CSS / Eleventy}{Jul. 2025 -- Present}
  {Ventura Coast Web Design LLC}{Moorpark, CA (Remote)}
  \resumeItemListStart
    \resumeItem{Founded and operate a web design business delivering modern, responsive websites and enhanced Google Business presence for local clients.}
    \resumeItem{Designed and developed reusable Eleventy templates, reducing project turnaround time and enabling consistent branding for marketing campaigns.}
    \resumeItem{Managed full sales cycle including lead generation, cold calling, proposals, and client onboarding.}
    \resumeItem{Optimized websites for SEO and performance, improving search rankings and user experience.}
    \resumeItem{Provided ongoing client support, including website maintenance, analytics reporting, and feature updates.}
  \resumeItemListEnd

\resumeSubheading
  {Software Engineer - Ruby on Rails / JavaScript / Go / AngularJS / Node.js}{Oct. 2021 -- Present}
  {LexisNexis Risk Solutions}{Boca Raton, FL (Remote)}
  \resumeItemListStart
    \resumeItem{Developed multiple Ruby on Rails applications supporting government agencies in delivering equitable law enforcement and justice solutions.}
    \resumeItem{Designed Git workflows and implemented CI/CD pipelines using GitHub Actions and Rancher, improving release speed and reliability.}
    \resumeItem{Provided 24/7 client support in an on-call rotation, resolving critical issues under pressure.}
    \resumeItem{Enhanced applications through Agile and Scrumban workflows, collaborating daily with product and project managers via Jira and Confluence.}
    \resumeItem{Partnered with QA teams to ensure comprehensive testing coverage and accurate automation results.}
    \resumeItem{Integrated and debugged RESTful APIs, including Google Earth, Google Maps, Odoo, and Twilio.}
    \resumeItem{Implemented Checkmarx software security scans across multiple applications, fostering a security-first development culture.}
    \resumeItem{Optimized AWS and Azure cloud environments, including Elasticsearch, S3, SDS, SES, Kibana, and Azure Cloud Services.}
    \resumeItem{Processed large cellular tower datasets in backend services using Ruby, Go, and Node.js to deliver actionable client insights.}
    \resumeItem{Built user-friendly front-end interfaces with Ruby ERB, JavaScript, TypeScript, jQuery, AngularJS, DataTables, and HTML/CSS.}
    \resumeItem{Migrated legacy Ruby on Rails applications to AngularJS and Node.js.}
    \resumeItem{Designed and maintained MySQL databases with a focus on scalability and clean schema design.}
  \resumeItemListEnd

\resumeSubheading
  {Software Engineer - Ruby on Rails / ReactJS / JavaScript}{May 2021 -- Aug. 2021}
  {Airship}{Birmingham, AL (Remote)}
  \resumeItemListStart
    \resumeItem{Worked at a Ruby on Rails and ReactJS development agency on small business projects, collaborating directly with clients.}
    \resumeItem{Delivered features and resolved bugs using Ruby on Rails, ReactJS, JavaScript, and jQuery.}
    \resumeItem{Managed CI/CD pipelines via GitHub Actions and deployed to Heroku and AWS.}
    \resumeItem{Executed sprint-based development, completing tickets aligned with client requirements using Jira and Notion.}
    \resumeItem{Collaborated closely with product managers and QA, producing proof-of-concept builds for clear alignment on deliverables.}
    \resumeItem{Planned and designed full features, including wireframes and task breakdowns.}
    \resumeItem{Migrated client infrastructure from Heroku to AWS, upgrading applications to modern stacks.}
  \resumeItemListEnd

\resumeSubheading
  {Software Engineer – Ruby on Rails / MagicTest / Capybara / JavaScript}{Sep. 2020 -- Apr. 2021}
  {Authorium (formerly City Innovate, Inc.)}{San Francisco, CA (Remote)}
  \resumeItemListStart
    \resumeItem{Developed a Ruby on Rails application (\textit{Solicitation Builder}) enabling government agencies to streamline procurement document creation.}
    \resumeItem{Built a comprehensive automated test suite with Capybara and MagicTest for a large monolithic application.}
    \resumeItem{Created an algorithm to auto-generate test fixtures by interacting with the application UI.}
    \resumeItem{Implemented high-impact features including weekly task digest emails and password reset functionality.}
    \resumeItem{Resolved UI and backend issues to improve performance and usability.}
    \resumeItem{Paired with engineers to share knowledge and maintain high code quality.}
    \resumeItem{Organized virtual team-building events, including social gatherings and coffee chats.}
  \resumeItemListEnd

\resumeSubheading
  {Computer Science Teacher - Django / Python / React / JavaScript}{May 2020 -- Sep. 2020}
  {BloomTech (formerly Lambda School)}{San Francisco, CA (Remote)}
  \resumeItemListStart
    \resumeItem{Taught daily projects and weekly sprints in Django, Python, data structures, and algorithms.}
    \resumeItem{Led a team of eight students in simulated work environments, facilitating daily standups.}
    \resumeItem{Provided 1:1 mentorship to support individual student growth and skill development.}
    \resumeItem{Reviewed and provided feedback on web projects to improve efficiency and maintainability.}
  \resumeItemListEnd

\resumeSubheading
  {Software Development Intern - Ruby on Rails / JavaScript / HTML5}{Feb. 2019 -- Sep. 2019}
  {Bullet Train, Inc.}{Los Angeles, CA}
  \resumeItemListStart
    \resumeItem{Completed a self-guided apprenticeship focused on mastering Ruby on Rails.}
    \resumeItem{Authored technical blog posts documenting the Ruby on Rails learning process.}
    \resumeItem{Identified and resolved client-facing bugs in the Bullet Train framework.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
  {BloomTech (formerly Lambda School)}{Sep. 2019 -- May 2020}
  {Full-Stack Web Development Certificate}{Remote}
\resumeSubheading
  {BCITO NZ}{Jan. 2013 -- Apr. 2016}
  {Certificate in Carpentry}{Christchurch, NZ}
\resumeSubheading
  {NCEA NZ}{Dec. 2009}
  {National Certificate of Educational Achievement (High School Diploma)}{Christchurch, NZ}
\resumeSubHeadingListEnd

\end{document}
